\documentclass{article}
\usepackage{bubblecv}
\usepackage[normalem]{ulem}

\begin{document}

\begin{cv}[avatar]{Ekrem Bayram}{Software Engineer}


    \cvsection[summary]{About Me}  %-----------------------------------------------------------

    My introduction to programming began in the 6th grade with BASIC. Subsequently, I acquired skills in HTML and CSS. During high school, I developed several applications using C\#, Microsoft SQL, and Windows Forms, some of which are available on my GitHub page. A summer school program provided the opportunity to work with Arduino, where I engineered a two-wheeled robot utilizing an ultrasonic sensor, a light-sensitive device that automated a lamp, and developed several games on a small LCD screen, including Snake, Pong, etc. Additionally, I expanded my knowledge to include JavaScript and created multiple websites, most of which are also accessible on my GitHub page.

    Growing up in Kazakhstan, I became fluent in Russian and have translated several applications into Russian, English, and Turkish, including \href{https://www.github.com/user-grinch/Cheat-Menu}{\uline{Cheat Menu}}, \href{https://www.play.google.com/store/apps/details?id=xeus.iconic}{\uline{Iconic}}, \href{https://www.polkuijken.medium.com/case-study-peek-launcher-220f0e505d51}{\uline{Peek Launcher}}, etc.

    My larger projects are listed on the following page of this document.

    \cvsection[work]{Work experience}  %------------------------------------------------------

    \begin{cvevent}[2020][present]
        \cvname{Game Developer}
        \cvdescription{Enot Games}
        \begin{itemize}
            \item Unity 3D
            \item C\#
            \item Unreal Engine
        \end{itemize}
    \end{cvevent}

    \cvseparator[2]
    \begin{cvevent}[2019][2020]
        \cvname{Assistant Database Engineer}
        \cvdescription{Akdeniz Elektrik Dağıtım A.Ş.}
        \begin{itemize}
            \item Microsoft SQL Server
            \item C\#
            \item WinForms
        \end{itemize}
    \end{cvevent}


    \cvsection[education]{Education}  %------------------------------------------------------

    \begin{cvevent}[2021][present]
        \cvname{Akdeniz University}
        \cvdescription{Bachelor of Engineering}
        \textbf{Additional Courses:}
        \begin{itemize}
            \item Unity 3D
            \item Arduino
            \item Game Art
        \end{itemize}
    \end{cvevent}


    \cvsection[target]{Projects}  %----------------------------------------------------------

    \begin{cvevent}[2023]
        \cvname{\href{https://www.github.com/ekrem-qb/math_scan}{\uline{Math Scanner}}}
        \begin{itemize}
            \item \textbf{Developed} an application that allows users to take screenshots and extract mathematical expressions using OCR (Optical Character Recognition).
            \item \textbf{Implemented} rendering of recognized mathematical expressions as LaTeX equations, enhancing the clarity and usability of extracted data.
            \item \textbf{Designed} the user interface with support for dark theme, ensuring the app adapts to system settings for improved user experience.
            \item \textbf{Created} functionality for automatic clipboard copying of recognized results, streamlining user workflow.
            \item \textbf{Adapted} the application for multiple platforms, including Windows and Linux, ensuring broad accessibility.
        \end{itemize}
    \end{cvevent}

    \cvseparator[2]
    \begin{cvevent}[2023]
        \cvname{\href{https://www.github.com/ekrem-qb/TeamsDownloader}{\uline{TeamsDownloader}}}
        \begin{itemize}
            \item \textbf{Developed} a command-line tool for downloading video recordings from Microsoft Teams.
            \item \textbf{Implemented} using .NET Core to ensure cross-platform compatibility and performance.
            \item \textbf{Utilized} Microsoft Graph API for secure and efficient access to Teams recordings.
            \item \textbf{Supported} downloading various video formats directly from Teams to local storage.
            \item \textbf{Improved} fetching efficiency by parallelizing, achieving a 20x speed boost (v0.0.2).
        \end{itemize}
    \end{cvevent}

    \cvseparator[2]
    \begin{cvevent}[2023]
        \cvname{Train}
        \begin{itemize}
            \item \textbf{Developed} a narrative-driven puzzle-adventure game inspired by \textit{Source Code} (2011) with mechanics similar to \textit{Twelve Minutes} (2021).
            \item \textbf{Implemented} a time loop mechanic for reliving an ten-minute sequence, enabling dynamic player choices and outcomes.
            \item \textbf{Designed} top-down point-and-click interactions and branching dialogue trees for immersive gameplay.
            \item \textbf{Engineered} multiple endings based on player decisions to enhance replayability.
            \item \textbf{Utilized} Unity and C\# for cross-platform development, ensuring smooth performance.
        \end{itemize}
    \end{cvevent}

    \cvseparator[2]
    \begin{cvevent}[2023]
        \cvname{Kirbilly PC Port}
        \begin{itemize}
            \item \textbf{Ported} Kirbilly from mobile to PC using Unreal Engine.
            \item \textbf{Adapted} controls and UI for mouse and keyboard, ensuring a smooth transition from touch-based input.
            \item \textbf{Reimplemented} procedural physics-based animations in Unreal Engine.
        \end{itemize}
    \end{cvevent}

    \cvseparator[2]
    \begin{cvevent}[2022]
        \cvname{\href{https://www.github.com/ekrem-qb/tshirt}{\uline{T-shirt designing app}}}
        \begin{itemize}
            \item \textbf{Developed} a t-shirt designing application inspired by \href{https://www.tisho.com}{\uline{tisho.com}} and \href{https://www.vsemayki.ru}{\uline{vsemayki.ru}}, integrated into a vending machine.
            \item \textbf{Implemented} a custom t-shirt design editor allowing users to create designs using text, predefined elements, or personal images.
            \item \textbf{Utilized} Python and AI for automatic background removal from photos.
            \item \textbf{Utilized} NodeJS to enable image uploads from a phone to a vending machine over Wi-Fi without an internet connection.
            \item \textbf{Utilized} Flutter for app development, ensuring smooth performance and cross-platform compatibility.
        \end{itemize}
    \end{cvevent}

    \cvseparator[2]
    \begin{cvevent}[2022]
        \cvname{\href{https://play.google.com/store/apps/details?id=com.EnotGame.Kirbilly}{\uline{Kirbilly}}}
        \begin{itemize}
            \item \textbf{Developed} a mobile action-adventure game featuring complex character abilities and diverse NPC behaviors.
            \item \textbf{Implemented} procedural movement, item interaction, and combat mechanics, including shooting, melee attacks, and fall damage effects.
            \item \textbf{Engineered} physics-based animations for realistic character interactions, enhancing immersion and dynamic responses to the game environment.
            \item \textbf{Designed} various NPC behaviors, such as patrolling gangsters, box-carrying workers, casual pedestrians, and explosive chickens, each with unique reactions to player actions.
            \item \textbf{Created} interactive level elements like movable objects, levers, platforms, and destructible items to enhance gameplay variety and challenge.
            \item \textbf{Adapted} game interactions for mobile devices, streamlining controls for picking up and throwing items, using weapons, and navigating levels.
            \item \textbf{Integrated} in-app purchases and ads, including rewarded ads for unlocking levels and removing ads, to enhance monetization.
            \item \textbf{Integrated} player analytics to track level progress, ad interactions, in-app purchases, and other key gameplay events.
            \item \textbf{Utilized} Unity and C\# for cross-platform development, ensuring smooth performance and efficient adaptation for mobile controls.
        \end{itemize}
    \end{cvevent}

    \cvseparator[2]
    \begin{cvevent}[2021]
        \cvname{2048 Miles per Hour}
        \begin{itemize}
            \item \textbf{Developed} a runner game combining mechanics of 2048 with high-speed gameplay, where stacking cubes accelerates the player's speed.
            \item \textbf{Implemented} intuitive swipe controls for seamless cube movement and stacking, enhancing user experience on mobile devices.
            \item \textbf{Engineered} a procedural track generation system featuring variable curves and layouts, inspired by Audiosurf, to maintain player engagement.
            \item \textbf{Enhanced} game challenge by adjusting track difficulty as the player's cube number and speed increase, with longer distances between objects and more obstacles.
            \item \textbf{Implemented} dramatic visual effects for player death, where cubes scatter forward, adding to the intensity and visual appeal of the game.
            \item \textbf{Utilized} Unity and C\# for cross-platform development, ensuring smooth performance and efficient adaptation for mobile controls.
        \end{itemize}
    \end{cvevent}

    \cvseparator[2]
    \begin{cvevent}[2021]
        \cvname{\href{https://github.com/ekrem-qb/Medicline}{\uline{Medical Record Management System}}}
        \begin{itemize}
            \item \textbf{Developed} a comprehensive medical record management system aimed at improving healthcare service efficiency for a health insurance company.
            \item \textbf{Implemented} features for storing, retrieving, and managing patient records, including personal information, medical history, and treatment plans.
            \item \textbf{Implemented} an employee permissions control panel to manage access rights and ensure data security.
            \item \textbf{Utilized} ElectronJS for creating a cross-platform desktop application with a seamless user experience.
            \item \textbf{Utilized} Firebase Database for efficient data storage and retrieval, allowing for quick access to patient records.
            \item \textbf{Utilized} Firebase Authentication for secure user authentication and management.
        \end{itemize}
    \end{cvevent}

    \cvseparator[2]
    \begin{cvevent}[2020]
        \cvname{Towers.io}
        \begin{itemize}
            \item \textbf{Developed} a mobile battle royale game featuring dynamic platform merging and strategic turret management.
            \item \textbf{Designed} a unique gameplay mechanic where players control a floating platform equipped with a turret, collecting and attaching neutral towers to increase size and firepower.
            \item \textbf{Implemented} smooth platform controls with realistic inertia and turning mechanics, providing an intuitive and engaging player experience.
            \item \textbf{Engineered} automatic turret targeting and firing systems, enhancing combat strategy and player engagement.
            \item \textbf{Created} diverse turret types including machine guns, rocket launchers, sniper turrets, and support towers to offer varied strategic options.
            \item \textbf{Developed} an intelligent enemy AI that adapts to the player's platform size and health, creating challenging and dynamic encounters.
            \item \textbf{Designed} a shrinking play zone to increase game intensity and urgency, inspired by classic battle royale mechanics.
            \item \textbf{Utilized} Unity and C\# for cross-platform development, ensuring seamless performance and efficient adaptation for mobile devices.
        \end{itemize}
    \end{cvevent}

    \cvseparator[2]
    \begin{cvevent}[2018]
        \cvname{\href{https://play.google.com/store/apps/details?id=com.ekrem.game.minecrash}{\uline{Minecrash}}}
        \begin{itemize}
            \item \textbf{Developed} an engaging arcade puzzle game.
            \item \textbf{Implemented} match-3 game mechanics, allowing players to align blocks and treasures to progress through levels and unlock special abilities.
            \item \textbf{Designed} challenging levels with increasing difficulty, incorporating various obstacles and power-ups to maintain player interest.
            \item \textbf{Engineered} an addictive gameplay loop with high replayability, encouraging players to achieve higher scores.
            \item \textbf{Integrated} in-game advertising seamlessly using Google AdMob and Appodeal, providing revenue opportunities while maintaining player immersion.
            \item \textbf{Utilized} Unity and C\# for seamless performance on Android platform, ensuring a smooth and responsive gameplay experience.
        \end{itemize}
    \end{cvevent}


    \cvsidebar %-----------------------------------------------------------------------------


    \cvsection[contact]{Contact}  %----------------------------------------------------------

    \begin{cvitem}[Envelope][4]
        \textbf{Email}\\
        \href{mailto:bayram.ekrem.007@gmail.com}{\texttt{\uline{bayram.ekrem.007@gmail.com}}}
    \end{cvitem}

    \cvseparator[3]
    \begin{cvitem}[Phone][4]
        \textbf{Phone}\\
        \href{tel:+905511819587}{\texttt{\uline{+90 551 181 9587}}}
    \end{cvitem}

    \cvseparator[3]
    \begin{cvitem}[Github][4]
        \textbf{GitHub}\\
        \href{https://www.github.com/ekrem-qb}{\texttt{\uline{github.com/ekrem-qb}}}
    \end{cvitem}

    \cvseparator[3]
    \begin{cvitem}[Linkedin][4]
        \textbf{LinkedIn}\\
        \href{https://www.linkedin.com/in/ekrem-qb}{\texttt{\uline{linkedin.com/in/ekrem-qb}}}
    \end{cvitem}


    \cvsection[skills]{Skills}  %-----------------------------------------------------------

    \begin{cvitem}
        C\#
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        Unity 3D
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        Unreal Engine
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        JavaScript
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        Flutter Dart
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        Arduino
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        HTML
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        CSS
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        LaTeX
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        NodeJS
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        ElectronJS
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        Git
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        Supabase
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        SQL
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        Firebase
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        REST API
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        Docker
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        C
    \end{cvitem}

    \cvseparator
    \begin{cvitem}
        C++
    \end{cvitem}


    \cvsection[languages]{Languages}  %--------------------------------------------------------

    \cvskill{Russian}{Native}{1.0}
    \cvskill{Turkish}{Proficient}{0.9}
    \cvskill{English}{Upper-Intermediate}{0.6}


\end{cv}

\end{document}

